Plant-pollintor networks worldwide are composed by the same specific building blocks

### 2021-05-19 Draft/Draft.Rmd
Update Draft.Rmd

  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
            data = pollinator_position_percentiles_filtered %>%
                          filter(position == pollinator_codes[i.pos]))

>>>>

  m <- lmer(percentil_its_GF ~ Node_FG + (1|study_id), #HERE WE NEED STUDY SYSTEM ONLY!! 
            data = pollinator_position_percentiles_filtered %>%
                          filter(position == pollinator_codes[i.pos]),
            control = lmerControl(optimizer ="Nelder_Mead")) # I changed the optimizer because motif 8 (i.pos = 3) caused convergence problems, max gradient = 0.0022 > 0.002.
